Cache is King: Presenting a Suite of Fast, Correlation Function Codes

### 2015-02-25 paper/ms.tex
Added a joint OpenMP scaling table for both mocks and theory (by copy-pasting the two individual OpenMP scaling files)
Fixed the Makefile. Updated the paper with the mocks plots

\begin{figure}[htbp]
\includegraphics[clip=true,width=\linewidth]{timings_Mr19_numpart}%
\caption{Scaling with particle number for \xir, \xirppi, \wprp }
\label{fig:scaling_numpart}
\end{figure}

\subsection{Scaling with \rmax}
\begin{figure}[htbp]
\includegraphics[clip=true,width=\linewidth]{timings_Mr19_rmax}%
\caption{Scaling with \rmax for \xir, \xirppi, \wprp }
\label{fig:scaling_rmax}
\end{figure}

\subsection{Scaling with OpenMP threads}
\begin{figure}[htbp]
\includegraphics[clip=true,width=\linewidth]{timings_Mr19_openmp}%
\caption{OpenMP scaling for \xir, \xirppi, \wprp }
\label{fig:scaling_openmp}
\end{figure}

\begin{table}
\centering
\caption{\footnotesize OpenMP scaling for the three codes. Efficiencies are defined 
as \texttt{Speedup/Nthreads}. Note, that \xir has super-linear scaling with \texttt{nthreads}
up to $\sim$ 10 threads.}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{ccccc} 
\toprule
\multirow{2}{*}{\textbf{Nthreads}}   &
\multicolumn{4}{c}{\textbf{Efficiency[\%]}} \\
\cmidrule(l{1.0em}r{1.0em}){2-5}
&
\multicolumn{1}{c}{$\boldsymbol{\xir}$}    &
\multicolumn{1}{c}{$\boldsymbol{\xirppi}$} &
\multicolumn{1}{c}{$\boldsymbol{\wprp}$}   & 
\multicolumn{1}{c}{$\boldsymbol{\xiofr}$}   \\
\midrule
\input{timings_Mr19_openmp} 
\bottomrule
\end{tabular}
\end{adjustbox}
\label{table:openmp}
\end{table}

>>>>

\begin{figure}[htbp]
\includegraphics[clip=true,width=\linewidth]{timings_Mr19_numpart}%
\caption{Scaling with particle number for \xir, \xirppi, \wprp and \xiofr}
\label{fig:scaling_numpart}
\end{figure}

\subsection{Scaling with \rmax}
\begin{figure}[htbp]
\includegraphics[clip=true,width=0.5\linewidth]{timings_Mr19_rmax}%
\includegraphics[clip=true,width=0.5\linewidth]{timings_Mr19_mocks_rmax}
\caption{Scaling with \rmax for \xir, \xirppi, \wprp and \xiofr}
\label{fig:scaling_rmax}
\end{figure}

\subsection{Scaling with OpenMP threads}
\begin{figure}[htbp]
\includegraphics[clip=true,width=0.5\linewidth]{timings_Mr19_openmp}%
\includegraphics[clip=true,width=0.5\linewidth]{timings_Mr19_mocks_openmp}
\caption{OpenMP scaling for \xir, \xirppi, \wprp and \xiofr}
\label{fig:scaling_openmp}
\end{figure}

\begin{table}
\centering
\caption{\footnotesize OpenMP scaling for the three codes. Efficiencies are defined 
as \texttt{Speedup/Nthreads}. Note, that \xir has super-linear scaling with \texttt{nthreads}
up to $\sim$ 10 threads.}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{ccccccccc} 
\toprule
\multirow{3}{*}{\textbf{Nthreads}}   &
\multicolumn{8}{c}{\textbf{Efficiency[\%]}} \\
\cmidrule(l{3em}r{3em}){2-9}

                                     &
\multicolumn{4}{c}{\textbf{Periodic Boxes}}  &
\multicolumn{4}{c}{\textbf{Spherical Geometry}}  \\
\cmidrule(l{1.0em}r{1.0em}){2-5}
\cmidrule(l{1.0em}r{1.0em}){6-9}
                                               &
\multicolumn{1}{c}{$\boldsymbol{\xir}$}        &
\multicolumn{1}{c}{$\boldsymbol{\xirppi}$}     &
\multicolumn{1}{c}{$\boldsymbol{\wprp}$}       & 
\multicolumn{1}{c}{$\boldsymbol{\xiofr}$}      &
\multicolumn{1}{c}{$\boldsymbol{DD(r_p,\pi)}$} &
\multicolumn{1}{c}{$\boldsymbol{DD(\theta)}$}  &
\multicolumn{1}{c}{$\boldsymbol{DR(r_p,\pi)}$} & 
\multicolumn{1}{c}{$\boldsymbol{DR(\theta)}$}   \\
\midrule
\input{timings_Mr19_openmp_theory_and_mocks}
\bottomrule
\end{tabular}
\end{adjustbox}
\label{table:openmp}
\end{table}
